---
title: "Tooth investiation"
author: "Jimi Damon"
date: "11/18/2015"
output: pdf_document
hitheme: tomorrow
mode: selfcontained
highlighter: highlight.js
framework: io2012
url:
  assets: ../../assets
  lib: ../../librariesNew
widgets: mathjax
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='./figure/',
                     warning=FALSE, message=FALSE)
```

## Overview

In this paper I will be examining the ToothGrowth dataset that comes
by default with the R programming language.  I will be constructing
plots that back up the statistical calculations that I will be making.

I loaded up basic libraries first and then examined the ToothGrowth
data by running 
```{r,echo=TRUE,eval=FALSE}
 ?ToothGrowth
```
From the query of the ToothGrowth data I found that there are 3
columns of data : one column is the length of teeth specified as len,
and two other columns are independent variables labeled as Supp ,
indicating the type of supplement and dose, indicating the dosage in milligrams.

In order to do a basic analysis on this data set , I will convert the 
ToothGrowth data frame into a tbl_df and make modifications using the

dplyr library.
```{r,echo=TRUE }
library(dplyr)
library(ggplot2)
tg <- tbl_df(ToothGrowth)
tg$dose <- factor(tg$dose)
```
From here I see that there are only two groups of supp. They are
```{r,echo=TRUE}
 unique(factor(tg$supp))
```

A quick plot of the data
```{r,echo=TRUE}
ggplot( tg, aes(x=dose,y=len,fill=supp)) + geom_bar(position=position_dodge(), stat="identity") 
```

A quick examination of the data
```{r,echo=TRUE}
knitr::kable(tg %>% group_by( supp, dose ) %>% summarize( len=mean(len) ) %>% arrange(dose))
```


### Statistical Tests
```{r,echo=TRUE}
t.test(len ~ supp, data=tg , paired=TRUE )
```

The samples are not equal as out calculated p-value is less than
0.05, the signifcance level.   Hence we reject the null-hypothesis
